---
title: "Lab 07 - Conveying the right message through visualisation"
author: "Rowan Kemmerly"
date: "5/1/2023"
output: github_document
---

### Load packages and data

```{r load-packages, message=FALSE}
library(tidyverse) 
library(lubridate)
```

### Exercise 1

```{r creating-data-frames}

maskcounties <- tribble(
  ~date, ~count,
  "7/12/2020", 25,
  "7/13/2020", 19.5,
  "7/14/2020", 19.5,
  "7/15/2020", 20,
  "7/16/2020", 19.5,
  "7/17/2020", 19.5,
  "7/18/2020", 20,
  "7/19/2020", 19.5,
  "7/20/2020", 19.75,
  "7/21/2020", 21.5,
  "7/22/2020", 20,
  "7/23/2020", 20,
  "7/24/2020", 20.5,
  "7/25/2020", 19,
  "7/26/2020", 19.5,
  "7/27/2020", 17,
  "7/28/2020", 16,
  "7/29/2020", 16.25,
  "7/30/2020", 16.5,
  "7/31/2020", 16,
  "8/1/2020", 16,
  "8/2/2020", 16,
  "8/3/2020", 16,
)

nomaskcounties <- tribble(
  ~date, ~count,
  "7/12/2020", 10,
  "7/13/2020", 9,
  "7/14/2020", 9.5,
  "7/15/2020", 9.75,
  "7/16/2020", 10,
  "7/17/2020", 9.5,
  "7/18/2020", 9.5,
  "7/19/2020", 9,
  "7/20/2020", 8.5,
  "7/21/2020", 8.5,
  "7/22/2020", 8.5,
  "7/23/2020", 8.5,
  "7/24/2020", 10,
  "7/25/2020", 10,
  "7/26/2020", 10,
  "7/27/2020", 9.5,
  "7/28/2020", 9.5,
  "7/29/2020", 9.5,
  "7/30/2020", 10,
  "7/31/2020", 9,
  "8/1/2020", 9,
  "8/2/2020", 9,
  "8/3/2020", 9,
)


```


### Exercise 2

```{r prepping-variables}

#converting "date" variables to actual date variable using lubridate:

maskcounties$date <- mdy(maskcounties$date)
nomaskcounties$date <- mdy(nomaskcounties$date)

typeof(maskcounties$date)

```


```{r new-visualization, fig.width=17}

newviz <- ggplot() +
  geom_line(data = maskcounties, aes(x = date, y = count, color = "With mask mandate")) + 
  geom_line(data = nomaskcounties, aes(x = date, y = count, color = "Without mask mandate")) +
  labs(title = "Kansas COVID-19 7-day rolling average of daily cases/per 100k population in 2020", subtitle = "Counties with a mask mandate vs. counties without mask mandates", x = "Date", y = "Average cases per 100k individuals", color = "County mask mandate status") +
  theme_classic() +
  scale_color_manual(values = c("With mask mandate" = "#fdae6b", "Without mask mandate" = "#a6bddb"))

newviz
```


### Exercise 3

Covid case numbers were always higher in counties with a mask mandate than in counties without a mask mandate. Now that both lines are using the same y axis, this is much clearer. 

### Exercise 4

This graph seems counterintuitive at first: you would think mask mandates would lead to lower numbers of Covid cases. However, it could be possible that transmission rates are higher in higher population counties, which could be a covariate with counties that have mask mandates (more population dense counties might be more likely to set mask mandates). So, even though this graph shows Covid numbers by 100k in population, it's still possible that numbers will be higher overall in more population dense areas, even with mask mandates in place. I've also read a decent number of articles (like this one: https://www.nytimes.com/2022/05/31/briefing/masks-mandates-us-covid.html) that talk about how wearing masks works, but that mandates don't work, so this graph would sort of go along with that kind of claim. 

